---
title: "List of Metrics"
author: "Chris Bielow <chris.bielow@fu-berlin.de>"
date: '`r Sys.Date()`'
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{List of Metrics}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


<!-- the TOC (table of content) would go here, but we create it manually to use this as a vignette
      - - > use 'toc: no' above to disable the TOC 
 -->

<a id="TOP"/>

<style type="text/css">
  p { 
    padding: 5px 0;
  }

  .helpText {
    clear: left;
  }
  
</style>

```{r setup, include=TRUE, echo=FALSE, results="asis"}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10)

lst_qcMetrics_ord = PTXQC:::getMetricsObjects()

txt_TOC = "# Table of Contents
  - [Overview](#Overview)
  - [Metrics](#Metrics)
"
txt_BODY = ""
for (qcm in lst_qcMetrics_ord)
{
  newname = gsub("(.*)\\(.*" , "\\1", gsub("[\\*~%]" , " ", gsub("[\\^\">]" , "", qcm$qcName))) 
  ## remove weird symbols (to serve as link)
  newname_lnk = gsub("[^a-zA-Z0-9]", "", newname)
  txt_TOC = paste0(txt_TOC, paste0("    - [", newname, "](#", newname_lnk, ")\n"))
  txt_BODY = paste0(txt_BODY, '\n
## ', newname, ' <a name="', newname_lnk, '"/>
\n
  <div class="helpText">', qcm$helpTextTemplate, '</div>
<p style="text-align: right"><a href="#TOP">-- back to top --</a></p>\n\n')
}

## print the TOC
cat(txt_TOC)

```

# Overview <a name="Overview"/>

The following metrics are implemented in PTXQC.<br>

Reasons why metrics might not appear in every report
 
 * applicable only to certain types of data, e.g. SILAC or TMT
 * metric was disabled manually using the YAML config file
 * missing input data (incomplete tables), e.g. only evidence.txt is present

 
Some metrics are incompletely named here, since they might contain (hithero unknown) thresholds.

# Metrics <a name="Metrics"/>
```{r metrics, echo=FALSE, results="asis"}
  cat(txt_BODY)
```

If the above list is empty, the vignette was not compiled (e.g. when viewing on GitHub).
Please see https://CRAN.R-project.org/package=PTXQC --> Vignettes for a compiled version.

