---
title: "Basic R-Usage Guide for PTXQC"
author: "Chris Bielow <chris.bielow@fu-berlin.de>"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: null
vignette: >
  %\VignetteIndexEntry{Basic R-Usage Guide for PTXQC}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Basic R-Usage Guide for PTXQC

This vignette serves as a quickstart guide for R users to create a report
from within R using PTXQC.

**Target Audience:** R users

Reports can be generated using the default configuration of PTXQC. 
See
```{r, eval=FALSE}
vignette("PTXQC-InputData", package = "PTXQC")
```
how a txt folder should look like.

## Generate a default report 

This is the most simple invokation of PTXQC::createReport().

```{r, eval=TRUE}
require(PTXQC)

## the next require() is needed to prevent a spurious error in certain R versions (might be a bug in R or a package)
## error message is:
##    Error in Scales$new : could not find function "loadMethod"
require(methods)

## specify a path to a MaxQuant txt folder
## Note: This folder needs to be complete (see 'vignette("PTXQC-InputData", package = "PTXQC")')
if (1) {
  ## we will use an example dataset from PRIDE (dataset 2 of the PTXQC publication)
  local_zip = tempfile(fileext=".zip")
  tryCatch({
	download.file("ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/11/PXD003133/txt_20min.zip", destfile = local_zip)
  }, error = function(err) {
    ## on Windows, one can get a 'cannot open URL' using the default method. So we try another
	download.file("ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/11/PXD003133/txt_20min.zip", destfile = local_zip, method= "internal")
  })
  unzip(local_zip, exdir = tempdir()) ## extracts content
  txt_folder = paste0(tempdir(),"/txt_20min")
} else {
  ## if you have local MaxQuant output, just use it
  txt_folder = "c:/Proteomics/MouseLiver/combined/txt"
}

r = createReport(txt_folder)

cat(paste0("\nReport generated as '", r$report_file, "'\n\n"))

```

## Generate a customized report

The report can be customized via a YAML configuration file.
For details, see

```{r, eval=FALSE}
vignette("PTXQC-CustomizeReport", package = "PTXQC")
```

After editing the YAML configuration to your needs, run the code below.

```{r, eval=FALSE}
require(PTXQC)
require(yaml)

## the next require() is needed to prevent a spurious error in certain R versions (might be a bug in R or a package)
## error message is:
##    Error in Scales$new : could not find function "loadMethod"
require(methods)

## specify a path to a MaxQuant txt folder
## Note: This folder can be incomplete, depending on your YAML config
if (1) {
  ## we will use an example dataset from PRIDE (dataset 2 of the PTXQC publication)
  local_zip = tempfile(fileext=".zip")
  download.file("ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/11/PXD003133/txt_20min.zip", destfile = local_zip)
  unzip(local_zip, exdir = tempdir()) ## extracts content
  txt_folder = paste0(tempdir(),"/txt_20min")
} else {
  ## if you have local MaxQuant output, just use it
  txt_folder = "c:/Proteomics/MouseLiver/combined/txt"
}

## use a YAML config inside the target directory if present
fh_out = getReportFilenames(txt_folder)
if (file.exists(fh_out$yaml_file))
{
  cat("\nUsing YAML config already present in target directory ...\n")
  yaml_config = yaml.load_file(input = fh_out$yaml_file)
} else {
  cat("\nYAML config not found in folder '", txt_folder, "'. The first run of PTXQC will create one for you.", sep="")
  yaml_config = list()
}

r = createReport(txt_folder, yaml_config)

cat(paste0("\nReport generated as '", r$report_file, "'\n\n"))

```

That's it.


