---
title: "ProTeomiX (PTX) Quality Control (QC) Report"
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---


<!-- the TOC (table of content) will go here - use 'toc: no' above to disable the TOC -->


<style type="text/css">
  p { 
    padding: 5px 0;
  }

  .helpSymbol {
    border: 1px solid #AAAAAA;
    padding: 3px;
    text-align: center;
    width: 100px;
  }
  .helpText {
    clear: left;
  }
  
</style>

```{r setup, include=FALSE}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10)
```

<a name="Overview"></a>

# Overview

**Quick guide**

  - navigate using the 'Table of Content' above or just scroll down
  - collapse sections by just clicking their name
  - click on the "&darr; Show Help" symbol to see a description for each metric and its scoring
  - edit the config `r paste0("file:///", gsub("\\\\", "/", rprt_fns$yaml_file))` to
     - set the report format (HTML, plainPDF, or both)
     - disable metrics
     - customize the order of metrics
     - set individual target thresholds
  - edit `r paste0("file:///", gsub("\\\\", "/", rprt_fns$filename_sorting))` to customize
     - the order of Raw files in plots and heatmap
     - abbreviations of Raw file names
  - edit the Html template `r paste0("file:///", gsub("\\\\", "/", html_template))` to
     - alter the look and feel of this report (e.g. colors, font and image sizes, help texts, etc.)
  - report bugs and file requests via the [GitHub issue tracker](https://github.com/cbielow/PTXQC/issues)
  - full PTXQC manual available [here](https://github.com/cbielow/PTXQC)

## HeatMap
```{r MQparams, echo=FALSE, results="asis"}
hm[["plot"]]
```

## Name Mapping
```{r nameMapping, echo=FALSE, results="asis"}
if(!is.null(pl_nameMapping) && (!any(is.na(pl_nameMapping)))) {
  cat(pl_nameMapping$htmlTable)
}
```


## Metrics
```{r metrics, echo=FALSE, results="asis"}

# Search for a suitable ggplot object which can be successfully converted to plotly
# returns empty list if no ggplot object found; the plotly object otherwise
findFirstPlotly = function(lst_qcMetrics_ord)
{
  pl_first = list()
  for (qcm in lst_qcMetrics_ord)
  {
    for (pl in qcm$plots)
    {
      if (any("ggplot" %in% class(pl)))
      {
        try({ pl_first = plotly::ggplotly(pl) })
      }
      if (length(pl_first) > 0) {
        return (pl_first)
      }
    }
  }
  return (pl_first)
}

pl_first = list()
if (enable_ploty)
{
  pl_first = findFirstPlotly(lst_qcMetrics_ord)  
}
## plot the first plotly object invisibly to include all the javascript libs etc...
## this MUST happen at this level (not within a scoped block etc) -- otherwise plotly code breaks
cat('<div style="display:none">')
##htmltools::tagList(pl_first)
cat('</div>')

plot_nr = 1

#for (qcm in lst_qcMetrics_ord[1:3])
for (qcm in lst_qcMetrics_ord)
{
  if (length(qcm$plots) == 0) next; # skip empty metrics
  #debug: 
  #cat(c("processing ", qcm$qcName))
  v_titles = qcm$getTitles(subtitle_sep = "\n<b>")
  plots = qcm$getPlots(withTitle = FALSE)
  if (length(v_titles) != length(plots)) {
    ## this is weird...
    stop("Number of titles is unequal to number of plots ...")
  }
  last_title = ""
  for (i in 1:length(v_titles))
  {
    if (last_title != v_titles[i]) {  ## print only new titles
      cat(paste0("\n\n### ", gsub("\n", "\n<br>", v_titles[i]), "</b>\n\n"))
    }
    if (i == 1) { ## print helpText only once
      cat(paste0('\n
<div>
<div class="helpSymbol">&darr; Show Help</div>
<div class="helpText">', qcm$helpText, "</div>
</div>"))
    }
    if (!is.na(qcm$htmlTable))
    { ## if there is an HTML table, prefer it over the plots
      cat(qcm$htmlTable)
      break;
    }
    
    pl = NA
    if (enable_ploty && any("ggplot" %in% class(plots[[i]]) && !("non_plotlyable" %in% names(plots[[i]]))))
    { ## try to convert to plotly
      try({ pl = plotly::ggplotly(plots[[i]]) })
    }
    if (!all(is.na(pl))) {
      #print(htmltools::tagList(list(pl))) ## adds javascript sources etc...
      html_file = paste0("p", plot_nr, ".html")
      dir.create('plots', showWarnings = FALSE)
      withr::with_dir('plots', saveWidget(pl, file = html_file, selfcontained = F, libdir = "lib"))
      cat(paste0('<iframe src="plots/', html_file, '" style="border: 0" width="910px" height="500px"></iframe>'))
      plot_nr = plot_nr + 1
    } else {
      ## static plots desired or not a ggplot object or error -- so just plot it non-interactive
      print(plots[[i]])
    } 
    
    
    cat("\n<br>\n")
    last_title = v_titles[i]
  }
  cat('\n<p style="text-align: right">[back to top](#Overview)</p>\n\n')
}
```



<script type="text/javascript">
jQuery(document).ready(function()
{
 // initially hide the help text
  jQuery(".helpText").hide();
  
  // toggle help text by clicking on the symbol
  jQuery(".helpSymbol").click(function(event)
  {
    var target = $( event.target );
    // "Show Help &darr;" is the first item in a <div> which encloses their section
    // so toggling its sibling (the actual text) will just leave the "Show Help &darr;" visible
    if ( target.is( "div" ) )
    {
      target.siblings().slideToggle(200);
      event.stopPropagation()
    }
  });
  
  
  // enable shortening the report
  jQuery(".section").click(function(event)
  {
    var target = $( event.target );
    // headings are the first item in a <div> which encloses their section
    // so toggling their siblings will just leave the heading visible
    if ( target.is( "h1, h2, h3, h4" ) )
    {
      target.siblings().slideToggle(200);
      event.stopPropagation()
    }
  });
});

</script>








