---
title: "PTXQC Quality Report"
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---

<style type="text/css">
  .content {
  padding: 5px 10px;
  background-color:#fafafa;
  }
  p { padding: 5px 0; }
</style>

<script type="text/javascript">
jQuery(document).ready(function()
{
  // initially hide the content (todo)
  jQuery(".content").hide();
  
  // enable shortening the report
  jQuery(".section").click(function(event)
  {
    var target = $( event.target );
    // headings are the first item in a <div> which encloses their section
    // so toggling their siblings will just leave the heading visible
    if ( target.is( "h1, h2" ) )
    {
      target.siblings().slideToggle(500);
      event.stopPropagation()
    }
  });
});
</script>

```{r setup, include=FALSE}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

# Overview
## Parameters
```{r MQparams}
rep_data$get("params")
```

## Name Mapping
```{r nameMapping}
rep_data$get("name_mapping")
```

## Heatmap
```{r heatmap}
rep_data$get("heatmap")
```

## Metrics
```{r metrics}
GPL_lst = rep_data$get("metric")
for (idx in sort(names(GPL_lst))) #[1:3])
{
  print(GPL_lst[[idx]] + ggtitle(""))
}
```

