---
title: "PTXQC List of Metrics"
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---


<!-- the TOC (table of content) will go here - use 'toc: no' above to disable the TOC -->


<style type="text/css">
  p { 
    padding: 5px 0;
  }

  .helpSymbol {
    border: 1px solid #AAAAAA;
    padding: 3px;
    text-align: center;
    width: 100px;
  }
  .helpText {
    clear: left;
  }
  
</style>

```{r setup, include=FALSE}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, fig.width=10)
```

# Overview

The following metrics are implemented in PTXQC.<br>

Reasons why metrics might not appear in every report
 
 * applicable only to certain types of data, e.g. SILAC or TMT
 * metric was disabled manually using the YAML config file
 * missing input data (incomplete tables), e.g. only evidence.txt is present

 
Some metrics are incompletely named here, since they might contain (hithero unknown) thresholds.

# Metrics
```{r metrics, echo=FALSE, results="asis"}
  for (qcm in lst_qcMetrics_ord)
  {
    newname = gsub("(.*)\\(.*" , "\\1", gsub("[\\*~%]" , " ", gsub("[\\^\">]" , "", qcm$qcName))) 
    cat(paste0('\n
## ', newname, '
\n\n
  <div class="helpText">', qcm$helpTextTemplate, '</div>
<p style="text-align: right">[back to top](#TOC)</p>\n\n'))
  }
```

