---
title: "PTXQC Quality Report"
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---

<style type="text/css">
  .content {
  padding: 5px 10px;
  background-color:#fafafa;
  }
  p { padding: 5px 0; }
</style>

<script type="text/javascript">
jQuery(document).ready(function()
{
  // initially hide the content (todo)
  jQuery(".content").hide();
  
  // enable shortening the report
  jQuery(".section").click(function(event)
  {
    var target = $( event.target );
    // headings are the first item in a <div> which encloses their section
    // so toggling their siblings will just leave the heading visible
    if ( target.is( "h1, h2" ) )
    {
      target.siblings().slideToggle(500);
      event.stopPropagation()
    }
  });
});
</script>

```{r setup, include=FALSE}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=TRUE, error=TRUE, message=TRUE, fig.width=8)
```

# Overview
## HeatMap
```{r MQparams, echo=FALSE, results="asis"}
hm[["plot"]]
```

## Name Mapping
```{r nameMapping, echo=FALSE, results="asis"}
pl_nameMapping[[1]]
```


# Metrics
```{r metrics, echo=FALSE, results="asis"}
  for (qcm in lst_qcMetrics_ord[1:5])
  {
    if (length(qcm$plots) == 0) next; ## skip empty metrics
    cat(paste0("\n## ", qcm$getTitles(), "\n"))
    cat(paste0("\n<div>", qcm$helpText, "</div>\n"))
    plots = qcm$getPlots(withTitle = FALSE)
    lapply(plots, print)
    cat("\n\n")
  }
```










