---
title: "PTXQC Quality Report"
output:
  html_document:
    mathjax: null
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---


<!-- the TOC will go here -->


<!-- requires internet, so we do not use it by default-->
  <script src="https://rawgit.com/wilddeer/stickyfill/master/dist/stickyfill.min.js"></script>
<!-- the same as above, but static -->

<style type="text/css">
  .content {
  padding: 5px 10px;
  background-color:#fafafa;
  }
  p { padding: 5px 0; }

  /* defined by Rmarkdown/Pandoc -- overwrite to get the full width */
  .main-container {
    max-width: 1400px;
  }
  
  /* the TOC div is generated by Pandoc -- we want it to float left*/
  #TOC {
      position: -webkit-sticky;
      position: sticky;
      top: 50px;
  }
  
  /* make the '# Overview' float -- do not use '#Overview {' -- alignment is different for some reason */
  .level1 {
    float: right;
  }
  
  .helpText {
    max-width: 600px;
  }
  
</style>

```{r setup, include=FALSE}
## global options
knitr::opts_chunk$set(echo=FALSE, warning=TRUE, error=TRUE, message=TRUE, fig.width=8)
```

<a name="Overview"></a>

# Overview


## HeatMap
```{r MQparams, echo=FALSE, results="asis"}
hm[["plot"]]
```

## Name Mapping
```{r nameMapping, echo=FALSE, results="asis"}
pl_nameMapping[[1]]
```


## Metrics
```{r metrics, echo=FALSE, results="asis"}
  #for (qcm in lst_qcMetrics_ord[1:3])
  for (qcm in lst_qcMetrics_ord)
  {
    if (length(qcm$plots) == 0) next; # skip empty metrics
    cat(paste0("\n### ", qcm$getTitles(subtitle_sep = "\n<b>"), "</b>\n"))
    cat(paste0('\n<div class="helpText">', qcm$helpText, "</div>\n"))
    plots = qcm$getPlots(withTitle = FALSE)
    lapply(plots, print)
    cat('\n<p style="text-align: right">[back to top](#Overview)</p>\n\n')
  }
```



<script type="text/javascript">
jQuery(document).ready(function()
{
  // initially hide the content (todo)
  jQuery(".content").hide();
  
  // enable shortening the report
  jQuery(".section").click(function(event)
  {
    var target = $( event.target );
    // headings are the first item in a <div> which encloses their section
    // so toggling their siblings will just leave the heading visible
    if ( target.is( "h1, h2" ) )
    {
      target.siblings().slideToggle(500);
      event.stopPropagation()
    }
  });
});

$(function() {
    $('#TOC').Stickyfill();
});

</script>








